Response to reviewers

### 2025-01-09 Manuscript/ecography_reponse_letter_2.tex
added glossary table

% TODO: add the table to the main text
% TODO: say we keep our definition of a trait as "measurable characteristic" (but that we use the more common defintion for the simulations)

>>>>

We've now added the the glossary table (supplementary table 1) to the main text as suggested with the definition of trait redefined as a characteristic (good catch!).
We did however keep our broader definition of a trait as opposed to \cite{violle2007let}'s (see response to first comment of Reviewer 3 above).
We have added this precision in the table:

\textit{Note that our definition of a trait is a generalisation of \cite{violle2007let,mcgill2006rebuilding,dawson2021traits}'s suggestions which is expanded to include traits beyond the ones used for functional ecology (macroevolution, palaeontology, microbiology, etc.).} Lines @@@

### 2025-01-09 Manuscript/main_ecography_R2.tex
added glossary table

>>>>

\begin{table}[ht]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2018disprity} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{2.5cm}p{4cm}p{5cm}p{5cm}}
Term in this paper & definition & in ecology & in macroevolution \\
\hline
Trait space & Matrix ($n \times d$) with a structural relation between rows and columns & Functional space, morphospace , etc. & Morphospace, traitspace, etc.  \\
\hline
Observations & Rows ($n$) & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs etc. \\
\hline
Dimensions & Columns ($d$) & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. \\
\hline
Traits & Columns subset ($b \times n$; $b \leq d$) & uni/multidimensional characteristic*; e.g. geographical location & uni/multidimensional characteristic; e.g. landmark coordinates \\
\hline
Group & Rows subset ($m \times d$; $m \leq n$) & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. \\
\hline
Metric & Statistic (i.e. a measure) & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index \\
\hline
Stressors & An algorithm removing a proportion of the observations & Introduction of invasive species, change of landscape use, climate change, pollution, experimental design, etc. & Mass extinction, Tectonic change, climate change, etc. \\
\hline
Stressors' intensity & The amount of observation removed (percentages) & Proportion of species affected, proportion of temperature change, etc. & Severity of mass extinction,  etc. \\
\hline
\end{tabular}
* Note that our definition of a trait is a generalisation of \cite{violle2007let,mcgill2006rebuilding,dawson2021traits}'s suggestions which is expanded to include traits beyond the ones used for functional ecology (macroevolution, palaeontology, microbiology, etc.).
\end{table}
